%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work and Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Contractor} % Job title
    {Elementiam -- Materials and Manufacturing} % Organization
    {Edmonton, Canada} % Location
    {Aug. 2021 - present} % Date(s)
    {
      \begin{cvitems}
        \item Electrical design of a control cabinet for a 5-axis CNC-based Hybrid Manufacturing platform
        \begin{itemize}
          \item Development of specifications, layout design, electrical schematics, design documentation, readyness for CSA approval
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Postdoctoral Fellow} % Job title
    {Additive Design and Manufacturing Systems Lab, MECE Department, University of Alberta} % Organization
    {Edmonton, Canada} % Location
    {Oct. 2018 - present} % Date(s)
    {
      \begin{cvitems}
        \item \emph{Primary project}: Robotic large-scale metal wire and arc additive manufacturing (WAAM) \newline
        in collaboration with InnoTech Alberta (Oct. 2018 - Apr. 2021)
        \begin{itemize}
          \item Procurement, commissioning and installation of robotic large-scale WAAM platforms
          \item Design and development of a ROS-based, harware-agnostic software toolchain for robotic large-scale AM -- from tool path to real-time computer-integrated execution
          \item Software design and development (robot trajectory planning and execution, process planning)
          \item Systems and sensor integration (hardware and software)
          \item Research on process planning methods, deposition parameter identification and optimization, and sensor-fusion-based and machine-learning-based process optimization and control
          \item Supervision of undergraduate and graduate students conducting research and development on process modeling, 
                in-situ process monitoring and control, process planning, system setup and integration, and other related topics
        \end{itemize}
        \item \emph{Secondary projects}:
        \begin{itemize}
          \item Automated repair of worn parts through 3D scanning and hybrid manufacturing
          \item Robotic ploymer AM
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    % TODO Come up with a better job title
    {Research Assistant} % Job title
    {Telerobotic and Biorobotic Systems Lab, ECE Department, University of Alberta} % Organization
    {Edmonton, Canada} % Location
    {Feb. 2018 - Sep. 2018} % Date(s)
    {
      \begin{cvitems}
        % TODO Think about a better description for this and improve all of below points
        \item {Introduction of the robot middleware \emph{Robot Operating System} (ROS) to the Telerobotic and Biorobotic Systems Lab}
        \begin{itemize}
          \item {Development of point streaming interfaces for industrial robots using ROS-Industrial}
          \item {Design and implementation of teleoperation for industrial robots using point streaming}
          \item {Design and implementation of an admittance controller for industrial robots}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Telerobotic and Biorobotic Systems Lab, ECE Department, University of Alberta} % Organization
    {Edmonton, Canada} % Location
    {Sep. 2013 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Research on PhD thesis topic: ``Novel sensing and actuation methods for needle steering in soft tissue with application to prostate brachytherapy''}
        \item{Developing novel methods for deflection estimation and control of a bevel-tipped needle during insertion}
        \item{Design of a 2-DOF experimental needle insertion robot (hardware and software in Matlab and Simulink Real-Time) for validation of deflection estimation and control algorithms}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {ECE Department, University of Alberta} % Organization
    {Edmonton, Canada} % Location
    {Sep. 2014 - Dec. 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Responsibilities: Instruction/supervision of laboratory and report/assignment grading}
        \begin{itemize}
          \item {\emph{Fall Term 2014}: ECE 210 -- Introduction to Digital Logic Design}
          \item {\emph{Winter Term 2015}: ECE 212 -- Introduction to Microprocessors}
          \item {\emph{Fall Term 2015, 2016 \& 2017}: ECE 464 -- Medical Robotics}
          \item {\emph{Winter Term 2016 \& 2017}: ENCMP 100 -- Computer Programming for Engineers}
        \end{itemize}
      \end{cvitems}
    }

  %---------------------------------------------------------
    \cventry
      {Research Assistant} % Job title
      {Institute of Technical Medicine (ITeM), Furtwangen University} % Organization
      {Schwenningen, Germany} % Location
      {Mar. 2013 - Aug. 2013} % Date(s)
      {
        \begin{cvitems}
          \item {Design and implementation of a Java-based patient simulator}
          \item {Re-implementation of various mathematical models of the cardiovascular system, heart, and respiratory system}
        \end{cvitems}
      }

  %---------------------------------------------------------
    \cventry
      {Research Assistant} % Job title
      {Telerobotic and Biorobotic Systems Lab, ECE Department, University of Alberta} % Organization
      {Edmonton, Canada} % Location
      {Sep. 2012 - Feb. 2013} % Date(s)
      {
        \begin{cvitems}
          \item {Research on Master's thesis titled: ``Development of an Intelligent Surgeon's Assistant for Needle Adjustment in Prostate Brachytherapy''}
          \item {Development of a virtual sensor for estimating needle deflection during insertion into soft tissue}
          \item {Design of an experimental setup for automated needle insertion}
        \end{cvitems}
      }

  %---------------------------------------------------------
    \cventry
      {Research Assistant} % Job title
      {Institute of Technical Medicine (ITeM), Furtwangen University} % Organization
      {Schwenningen, Germany} % Location
      {Nov. 2011 - Aug. 2012} % Date(s)
      {
        \begin{cvitems}
          \item {Implementation of a Java-based tool for real-time plotting of a ventilation support simulator for Android mobile devices}
        \end{cvitems}
      }

  %---------------------------------------------------------
  \cventry
    % TODO (maybe) rename the job title to visiting student or something
    {Visiting Student} % Job title
    {University of Canterbury} % Organization
    {Christchurch, New Zealand} % Location
    {Oct. 2010 - Mar. 2011} % Date(s)
    {
      \begin{cvitems}
        \item {Research for Bachelor's thesis titled:} ``Software Development for an Autonomously Operating Robot Truck for the Location and Recovery of Objects''
        \item {Research and development of image processing methods for object detection under noisy conditions}
        % TODO finish below
        \item {Development of a state-machine-based algorithm for automatic manouvering and decision making}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
  % TODO (maybe) rename the job title to visiting student or something
  {Intern} % Job title
  {Aesculap AG} % Organization
  {Tuttlingen, Germany} % Location
  {Mar. 2009 - Aug. 2009} % Date(s)
  {
    \begin{cvitems}
      \item {Development of microcontroller software in C for automatic detection of various types of surgical drills}
      \item {Design and assembly of electronic circuits}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
