%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  %\cvparagraph{}
  \cvpub
    {Journals}{
      \begin{longtable}{p{0.5cm} p{\textwidth - 0.5cm}}
        [1] & \underline{T. Lehmann}, A. Jain, Y. Jain, H. Stainer, T. Wolfe, H. Henein, A. J. Qureshi, ``Concurrent geometry- and material-based process identification and optimization for robotic CMT-based wire arc additive manufacturing,'' \emph{Materials \& Design}, vol. 194, p. 108841, Sep. 2020. \\\relax
        [2] & \underline{T. Lehmann}, R. Sloboda, N. Usmani and M. Tavakoli, ``Model-Based Needle Steering in Soft Tissue via Lateral Needle Actuation,'' in \emph{IEEE Robotics and Automation Letters}, vol. 3, no. 4, pp. 3930-3936, Oct. 2018. Also, selected for presentation at the IEEE/RSJ International Conference on Intelligent Robots and Systems, Madrid, Spain, 2018. \\\relax
        [3] & \underline{T. Lehmann}, R. Sloboda, N. Usmani, and M. Tavakoli, ``Human-machine collaboration modalities for semi-automated needle insertion into soft tissue,'' \emph{IEEE Robotics and Automation Letters}, vol. 3, no. 1, pp. 477–483, 2018. \\\relax
        [4] & \underline{T. Lehmann}, C. Rossa, N. Usmani, R. Sloboda, and M. Tavakoli, ``Intraoperative Tissue Young’s Modulus Identification During Needle Insertion Using a Laterally Actuated Needle,'' \emph{IEEE Transactions on Instrumentation and Measurement}, vol. 67, no. 2, pp. 371–381, 2018. \\\relax
        [5] & \underline{T. Lehmann}, C. Rossa, N. Usmani, R. Sloboda, and M. Tavakoli, ``Deflection modeling for a needle actuated by lateral force and axial rotation during insertion in soft phantom tissue,'' \emph{Mechatronics}, vol. 48, pp. 42–53, 2017. \\\relax
        [6] & \underline{T. Lehmann}, C. Rossa, N. Usmani, R. Sloboda and M. Tavakoli. ``A real-time estimator for needle deflection during insertion into soft tissue based on adaptive modeling of needle-tissue interactions''. \emph{IEEE/ASME Transactions on Mechatronics}, vol. 21, issue 6, pp. 2601--2612, 2016. \\\relax
        [7] & C. Rossa, \underline{T. Lehmann}, R. Sloboda, N. Usmani and M. Tavakoli. ``A data-driven soft sensor for needle deflection in heterogeneous tissue using just-in-time modelling''. \emph{Medical \& Biological Engineering \& Computing}, pp. 1--14, 2016. \\\relax
        [8] & J. Kretschmer, B. Laufer, \underline{T. Lehmann}, P. Stehle, D. Redmond, and K. M\"oller. ``Ein softwarebasierter Patientensimulator zur Evaluierung medizinischer Entscheidungssysteme (A software-based patient simulator to evaluate medical decision support systems)''. \emph{at -- Automatisierungstechnik}, vol. 64, issue 11, pp. 878--893, 2016. \\\relax
        [9] & P. Stehle, \underline{T. Lehmann}, D. Redmond, K. M\"{o}ller, and J. Kretschmer, ``A java based simulator with user interface to simulate ventilated patients,'' \emph{Current Directions in Biomedical Engineering}, vol. 1, no. 1, pp. 423--427, 2015. \\\relax
        [10] & \underline{T. Lehmann}, M. Tavakoli, N. Usmani and R. Sloboda. ``Force-Sensor-Based Estimation of Needle Tip Deflection in Brachytherapy''. \emph{Journal of Sensors}, vol. 2013, 2013.
    \end{longtable}
  }
  %\clearpage
  \cvpub
    {Conferences (peer-reviewed)}{
      \begin{longtable}{p{0.5cm} p{\textwidth - 0.5cm}}
        [11] & \underline{T. Lehmann}, C. Rossa, N. Usmani, R. Sloboda and M. Tavakoli. ``Needle path control during insertion in soft tissue using a force-sensor-based deflection estimator''. \emph{Proceedings of the 2016 IEEE International Conference on Advanced Intelligent Mechatronics}, Banff, Canada, July 12--15, 2016, pp. 1174--1179. \\\relax
        [12] & J. Kretschmer, \underline{T. Lehmann}, D. Redmond, P. Stehle and K. M\"oller, ``A Modular Patient Simulator for Evaluation of Decision Support Algorithms in Mechanically Ventilated Patients'', \emph{XIV Mediterranean Conference on Medical and Biological Engineering and Computing 2016 (MEDICON 2016)}, 2016. \\\relax
        [13] & \underline{T. Lehmann}, C. Rossa, N. Usmani, R. Sloboda and M. Tavakoli. ``A virtual sensor for needle deflection estimation during soft-tissue needle insertion''.  \emph{Proceedings of the 2015 IEEE International Conference on Robotics and Automation}, Seattle, USA, 2015, pp. 1217--1222. \\\relax
        [14] & T. Nguyen, \underline{T. Lehmann}, J. Kretschmer and K. M\"{o}ller, ``Bringing model based ventilation therapy to the bedside'', \emph{2013 ICME International Conference on Complex Medical Engineering}, Beijing, China, 2013, pp. 666-669.
      \end{longtable}
    }
%---------------------------------------------------------
\end{cventries}
